Evolving Motion Machines

### 2019-04-25 Final/paper.tex
Removed unnecessary files from paper folder

\section{Implementation}
With the goal of moving as far as possible in each generation, an appropriate environment must first exist to evaluate within.
To this end, Unity Engine is used

>>>>

\section{Implementation}
With the goal of moving as far as possible in each generation, an appropriate environment must first exist to evaluate within.
Further, within the environment there are a list of features that must be included to support the evaluation.
First and foremost is the ability to deserialize a given genotype into a phenotype, or agent, to be evaluated.
Also needed is the inverse serialization ability.
Then, agents need some physics simulator to operate within and source the evaluation of exactly how much distance has been covered.

To this end, Unity Engine is used
